Hypercoercions and a Framework for Equivalence of Cast Calculi

### 2019-10-27 paper.tex
missing comma
minor edits

\begin{definition}[Values and cast results for the \effCEK{C} machine] 
\label{def:values-effCEK}
  \[
  \begin{array}{lrcl}
  \stxrule{v}{Values}{
    \hcvOOtt \mid
    \hcvOOfun{c}{\mathcal{E}}{x}{e}{c} \mid
    \hcvOOcons{v}{c}{v}{c} \mid
    \hcvOOinl{v}{c} \mid
    \hcvOOinr{v}{c} \mid
    \hcvOOinj{I}{v}
  }
\stxrule{r}{Cast results}{
  \rOOsucc{v} \mid
  \rOOfail{l}
}
  \end{array}
  \]
\end{definition}

@@

Cast results ($r$) are the same as for \ineffCEK. 
Value typing ($\judgeType{v}{T}$) is defined in the obvious way.

@@

%<<<<<<< HEAD
\effCEK{C} is a space-efficient CEK machine parameterized over the Cast ADT ($C$).  
The key differences between \effCEK{C} and \ineffCEK\ are the places where 
casts can accumulate at runtime, that is, values and continuations. We discuss 
above the difference in values (Definition~\ref{def:values-effCEK}).

\begin{definition}[Continuations for the \effCEK{C} machine] 
\label{def:values-effCEK}
%=======
%\begin{figure}
%%  Syntax
%>>>>>>> bd39888b0287dbef61e981bd0e79bc8822fc85ce
  \[
  \begin{array}{lrcl}
% \stxrule{r}{cast results}{
%   \rOOsucc{v} \mid
%   \rOOfail{l}
% }
% \stxrule{s}{states}{
%   \sOOinspect{e}{\mathcal{E}}{\kappa} \mid{}
%   \sOOreturn{v}{\kappa} \mid{}
%   \sOOhalt{o}
% }
  \stxrule{\kappa}{Continuation}{
    \kOOcast{c}{k}
  }
  \stxrule{k}{Pre-continuations}{
    \kOOmt \mid{}
    \kOOconsI{T}{T}{e}{\mathcal{E}}{\kappa} \mid
    \kOOconsII{T}{T}{v}{\kappa} \mid
    \kOOinl{T}{T}{\kappa}
  }
  \stxrulecont{
  	\kOOinr{T}{T}{\kappa} \mid
    \kOOappI{e}{\mathcal{E}}{\kappa} \mid
    \kOOappII{v}{\kappa} \mid
    \kOOcar{\kappa} \mid
    \kOOcdr{\kappa}
  }
  \stxrulecont{
    \kOOcaseI{e}{e}{\mathcal{E}}{\kappa} \mid
    \kOOcaseII{v}{e}{\mathcal{E}}{\kappa} \mid
    \kOOcaseIII{v}{v}{\kappa}
  }
  \end{array}
  \]
\end{definition}

Let $\kappa$ range over continuations and let $k$ range over
pre-continuations.
%
Pre-continuations are like the continuations in \ineffCEK{}, but there is no 
constructor for casts.
%
A continuation is now a pre-continuation prefixed with a cast.
%
Continuations in \ineffCEKD{} have zero or more casts at the top.  In 
\effCEK{C}, however, every continuation has exactly one cast at the top.
Continuations in \ineffCEK\ that have no casts at the top correspond
to continuations in \effCEK{C}\ whose casts are identities.
Continuations in \ineffCEK\ that have many casts at the top correspond
to continuations in \effCEK{C}\ where those casts are composed by
$seq(c,c)$.

@@

Fig.~\ref{fig:bisim-SC-D} defines the bisimulation relation
$s_1 \approx s_2$, where $s_1 \in \effCEK{C}$ and $s_2 \in \ineffCEKD{}$.
It is the smallest congruence relation that also includes the
pairs induced by the rules in Fig.~\ref{fig:bisim-SC-D}.
%
The relation is mutually defined on continuations, written $\kappa
\approx \kappa : T$, where $T$ is their source type, and values, written $v 
\approx v : T$, where $T$ is their type.
%
If $k \approx \kappa : T$, adding an identity cast on top of $k$ gives a 
related continuation. This handles the way in which
\effCEK{C} uses $wrap$ to push identity coercions onto continuations
whereas \ineffCEKD{} does not.
%
We remark that this bisimulation relation is unusual in that it uses
some ADT operations in its definition, such as $id$, $cast$, and
$seq$, which is necessary because \effCEK{C} and the bisimulation
is parameterized over the Cast ADT.
%
%\todo[inline]{The use of ``wrap'' obscures this explanation.
%  Consider getting rid of wrap by inlining it. -JS
%\\---\\
%I agree that inlining wrap and ext can improve readability of $\kappa \approx 
%\kappa$, but this would make latex different from Agda, is it alright?
%-KC
%\\---\\
%Yes, that is alright. Inlining is really a trivial change.
%-JS
%}
%
If $\kOOcast{c}{k_1} \approx \kappa_2 : T$, extending the right-hand
side with a cast $T_1 \Rightarrow^l T_2$ and sequencing
$cast(T_1,l,T_2)$ with $c$ on the left-hand side, produces related
continuations. This takes care of the difference between
the transition rules for $e \langle T_1 \Rightarrow^l T_2$
on the two machines.

@@

%Before proving the weak bisimulation between \effCEK{C} and \ineffCEKD, we 
%introduce one more definition. $s_1 \approx^{*} s_2$ means we will get $s_1 
%\approx s_2$ after more transition steps in \ineffCEKD.
%
%\begin{definition}[$s \approx^{*} s$]
%Given any two states $s_1$ and $s_2$, we write $s_1 \approx^{*} s_2$
%if and only if there exists a state $s_2' \in \text{\ineffCEKD}$ such
%that
%\[
%\judgeDreduceTrans{s_2}{s_2'}
%\;\text{and}\;
%s_1 \approx s_2'
%\]
%\end{definition}
%
%%\todo[inline]{Explain that this is an unusual formulation of a weak
%%  bisimulation.  We promise it will all be OK regarding how it is used
%%  in the correctness proof for S(C). -JS}
%
%The lemma below formulate the weak bisimulation between \effCEK{C} and 
%\ineffCEKD. It is unusual because we use $s \approx s$ in premise while $s 
%\approx^{*} s$ in conclusion. As we will show in the correctness proof for 
%\effCEK{C}, however, this formulation is fine for our purpose.

\begin{lemma}[Weak Bisimulation between \effCEK{C} and \ineffCEKD]
  \label{thm:SD-bisim}
  Assume $C$ implements Lazy D Cast ADT
  and $C$ is a monoid
  and $cast(T,l,T)=id(T)$,
  $s_{1} \in \text{\effCEK{C}}$,
  $s_{2} \in \text{\ineffCEKD}$,
  $s_{1} \approx s_{2}$,
\begin{enumerate}
	\item If $\judgeSreduce{C}{s_1}{s_3}$ then
	$\judgeDreduceTrans{s_2}{s_4}$ and $s_3 \approx s_4$ for some $s_4$.
	\item If $\judgeDreduce{s_2}{s_4}$ then
	$\judgeSreduceTrans{C}{s_1}{s_3}$,
	$\judgeDreduceTrans{s_4}{s_5}$, and
	$s_3 \approx s_5$ for some $s_3$ and $s_5$.
	\item $s_1 = \sOOhalt{o}$ if and only if  $s_2 = \sOOhalt{o}$
\end{enumerate}
%\begin{enumerate}
%  \item $s_1 = \sOOhalt{o}$ if and only if  $s_2 = \sOOhalt{o}$
%%  \item If $s_2 = \sOOhalt{o}$ then $s_1 = \sOOhalt{o}$
%  \item If $\judgeSreduce{C}{s_1}{s_3}$ 
%    then $\judgeDreduce{s_2}{s_4}$ 
%    and  $s_3 \approx^{*} s_4$
%    for some $s_4$
%  \item If $\judgeDreduce{s_2}{s_4}$
%    then $\judgeSreduce{C}{s_1}{s_3}$ 
%    and  $s_3 \approx^{*} s_4$
%    for some $s_3$
%\end{enumerate}
%{\color{red}
%  Jeremy's attempt to reformulate in a more standard way that
%  remains equivalent:
%\begin{enumerate}
%\item If $\judgeSreduce{C}{s_1}{s_3}$ then
%  $\judgeDreducePlus{s_2}{s_4}$ and $s_3 \approx s_4$ for some $s_4$.
%\item If $\judgeDreduce{s_2}{s_4}$ then
%  $\judgeSreduce{C}{s_1}{s_3}$,
%  $\judgeDreduceTrans{s_4}{s_5}$, and
%   $s_3 \approx s_5$ for some $s_3$ and $s_5$.
%\item $s_1 = \sOOhalt{o}$ if and only if  $s_2 = \sOOhalt{o}$
%\end{enumerate}
%}
%Or diagrammatically, 
%  \[\begin{array}{clclc}
%  s_{1} & \longrightarrow_{\text{\effCEK{C}}} & s_1'\\
%  \rotatebox[origin=c]{90}{$\approx$} 
%  & & & \;\;\;\rotatebox[origin=c]{-20}{$\approx$} \\
%  s_{2} & 
%  \longrightarrow_{\text{\ineffCEKD}} & s_2' &
%  \longrightarrow^{*}_{\text{\ineffCEKD}} & s_2'' \\
%  \end{array}\]
\end{lemma}
\begin{proof}
  Part (1) follows from the definition of $s \approx s$.
  Part (2) and (3) are more interesting. 
  By the definition of $s \approx s$, it is straightforward to prove 
  $\judgeSreduce{C}{s_1}{s_3}$ if and only if $\judgeDreduce{s_2}{s_4}$.
  So we can prove two parts together by showing that 
  \[
  \text{if}\; s_{1} \approx s_{2}
  \;\text{and}\;\judgeSreduce{C}{s_1}{s_3}
  \;\text{and}\;\judgeDreduce{s_2}{s_4}
  \;\text{then}\; s_3 \approx^{*} s_4.
  \]
  To put it another way, our goal is to prove that 
  one reduction step in \effCEK{C} corresponds to
  one or more steps in \ineffCEKD.  
  Although there are many cases, the general idea is the same.
  Consider
  \[
  \sOOreturn{\hcvOOcons{v_{11}}{c_{11}}{v_{12}}{c_{12}}}{
    wrap(\kOOcar{\kappa})
  }
  \approx
  \sOOreturn{v_2}{\kOOcar{\kappa}}
  \]

@@

\begin{corollary}[Correctness of \effCEK{C}]
  \label{thm:SD-equiv}
  Suppose $C$ is an instance of the Cast ADT
  and the \lazyD{} ADT, $C$ is a monoid
  and $cast(T,l,T)=id(T)$.
  If $\judgetype{\emptyset}{e}{T}$ and $o : T$, then
  \[
    \text{\evalEqv{\effCEK{C}}{\ineffCEKD}}
  \]
\end{corollary}
\begin{proof}
	By the definitions of $eval$, we need to show 
	\[
	\judgeSreduceTrans{C}{\sOOinspect{e}{\emptyset}{wrap(\kOOmt)}}{
		\sOOhalt{o}
	}
	\;\text{if and only if}\;
	\judgeSreduceTrans{C}{\sOOinspect{e}{\emptyset}{\kOOmt}}{
		\sOOhalt{o}
	}
	\]
	Obviously, the initial states are related in the bisimulation relation.
	\[
	\sOOinspect{e}{\emptyset}{wrap(\kOOmt)}
	\approx
	\sOOinspect{e}{\emptyset}{\kOOmt}
	\]
	So we can generalize our goal, and prove that if $s_1 \approx s_2$
	\[
	\judgeSreduceTrans{C}{s_1}{\sOOhalt{o}}
	\;\text{if and only if}\;
	\judgeSreduceTrans{C}{s_2}{\sOOhalt{o}}
	\]

@@

\begin{proposition}[Equivalence of Two \lazyD{} Cast ADTs]
  \label{thm:surely-lazyD-eqv}
  Assume $C_1$ and $C_2$ implements Lazy D Cast ADT,
  \[
  eval_{\mathcal{S}(C_1)} = eval_{\mathcal{S}(C_2)}.
  \]
\end{proposition}
\begin{proof}
  Without lose of generality, assume $\judgeSreduce{C_1}{e}{o}$, prove 
  $\judgeSreduce{C_2}{e}{o}$.\\
  By the definition of $eval_{\mathcal{S}(C)}$, we know 
\[
\judgeSreduceTrans{C_2}{\sOOinspect{e}{\emptyset}{wrap(\kOOmt)}}{\sOOhalt{o}}
\]
  By induction on this reduction sequence and Lemma~\ref{thm:CEKS-bisim}, we 
  have 
\[
\judgeSreduceTrans{C_2}{\sOOinspect{e}{\emptyset}{wrap(\kOOmt)}}{\sOOhalt{o}}
\]
  that is, $\judgeSreduce{C_2}{e}{o}$
\end{proof}

@@

The $L$ cast representation is defined in \figref{fig:L-instance-LazyD}.
Casts in $L$ are lists of steps ($s$), where every step is like a cast in 
\ineffCEKD. The function $applyCast$ applies steps from left to right. Steps are 
restricted by its typing rule such that its source and target are different. This 
restriction is necessary to show $cast(T,l,T) = id(T)$. With this representation
of casts, the operators $id$ and $seq$ are the empty list of steps and list
append on casts respectively.

@@

\begin{lemma}[$L$ is Correct wrt. \ineffCEKD]
  \label{lem:L-correct}
  \[
  \text{\evalEqv{\effCEK{L}}{\ineffCEKD}}
  \]
\end{lemma}
\begin{proof}
  Immediately from
  Correctness of \effCEK{C} (Lemma~\ref{thm:SD-equiv}) and 
  Properties of $L$ (Proposition~\ref{thm:L-LazyD-monoid}).
\end{proof}

@@

  \fbox{$applyMiddle(v,\ell,m) = r$}
  \[
  \begin{array}{rclr}
  \funrule{applyMiddle(\hcvOOtt,\ell,\POOunit)}{\rOOsucc{\hcvOOtt}}{}
  \funrule{applyMiddle(\hcvOOfun{c_1}{\mathcal{E}}{x}{e}{c_2}\ell,\POOfun{c_3}{c_4})}{
    \rOOsucc{(\hcvOOfun{(c_3 \fatsemi^\ell c_1)}{\mathcal{E}}{x}{e}{(c_2 
    \fatsemi^\ell c_4)})}
  }{}
  \funrule{applyMiddle(\hcvOOcons{v_1}{c_1}{v_2}{c_2},\ell,\POOprod{c_3}{c_4})}{
    \rOOsucc{(\hcvOOcons{v_1}{(c_1 \fatsemi^\ell c_3)}{v_2}{(c_2 
    \fatsemi^\ell c_4)})}
  }{}
  \funrule{applyMiddle(\hcvOOinl{v}{c_1},\ell,\POOsum{c_3}{c_4})}{
    \rOOsucc{(\hcvOOinl{v}{(c_1 \fatsemi^\ell c_3)})}
  }{}
  \funrule{applyMiddle(\hcvOOinr{v}{c_2},\ell,\POOsum{c_3}{c_4})}{
    \rOOsucc{(\hcvOOinr{v}{(c_2 \fatsemi^\ell c_4)})}
  }{}
  \funrule{applyMiddle(v,l,m)}{
    \rOOfail{l}
  }{
    \sidecond{v \not\smile m}
  }
  \end{array}
  \]

@@

We also present steps toward the first framework for proving the
correctness of cast representations.
%
The framework includes abstract data types for cast representations
(Cast ADT and its refinement Lazy D Cast ADT), a parameterized abstract machine
\effCEK{C}, and a theorem which states that \effCEK{C} is equivalent
to $D$ when $C$ is a Lazy D Cast ADT.
%
%The Lazy D Cast ADT refines the Cast ADT. 
%
We conjecture that Lazy D
threesomes and Lazy D coercions in normal form are instances of the
Lazy D Cast ADT.

>>>>

\begin{definition}[Values and cast results for the \effCEK{C} machine] 
\label{def:values-effCEK}
  \[
  \begin{array}{lrcl}
  \stxrule{v}{Values}{
    \hcvOOtt \mid
    \hcvOOfun{c}{\mathcal{E}}{x}{e}{c} \mid
    \hcvOOcons{v}{c}{v}{c} \mid
    \hcvOOinl{v}{c} \mid
    \hcvOOinr{v}{c} \mid
    \hcvOOinj{I}{v}
  }
\stxrule{r}{Cast results}{
  \rOOsucc{v} \mid
  \rOOfail{l}
}
\stxrule{\mathcal{E}}{Environments}{
	\text{a partial function}\;\{\langle x , v \rangle , \dots \}
}

  \end{array}
  \]
\end{definition}

@@

Cast results ($r$) and environments ($\mathcal{E}$) are the same as for 
\ineffCEK. 
Value typing ($\judgeType{v}{T}$) is defined in the obvious way.

@@

\effCEK{C} is a space-efficient CEK machine parameterized over the Cast ADT ($C$).  
The key differences between \effCEK{C} and \ineffCEK\ are the places where 
casts can accumulate at runtime, that is, values and continuations.
The differences regarding values was discussed 
above (Definition~\ref{def:values-effCEK}).
We define contiuations below, with $\kappa$ ranging over continuations
and $k$ ranging over pre-continuations.
%
Pre-continuations are like the continuations in \ineffCEK{}, but there is no 
constructor for casts.
%
A continuation is now a pre-continuation prefixed with a cast.

\begin{definition}[Continuations for the \effCEK{C} machine] 
\label{def:values-effCEK}
  \[
  \begin{array}{lrcl}
  \stxrule{\kappa}{Continuation}{
    \kOOcast{c}{k}
  }
  \stxrule{k}{Pre-continuations}{
    \kOOmt \mid{}
    \kOOconsI{T}{T}{e}{\mathcal{E}}{\kappa} \mid
    \kOOconsII{T}{T}{v}{\kappa} \mid
    \kOOinl{T}{T}{\kappa}
  }
  \stxrulecont{
  	\kOOinr{T}{T}{\kappa} \mid
    \kOOappI{e}{\mathcal{E}}{\kappa} \mid
    \kOOappII{v}{\kappa} \mid
    \kOOcar{\kappa} \mid
    \kOOcdr{\kappa}
  }
  \stxrulecont{
    \kOOcaseI{e}{e}{\mathcal{E}}{\kappa} \mid
    \kOOcaseII{v}{e}{\mathcal{E}}{\kappa} \mid
    \kOOcaseIII{v}{v}{\kappa}
  }
  \end{array}
  \]
\end{definition}

Continuations in \ineffCEKD{} have zero or more casts at the top.  In 
\effCEK{C}, however, every continuation has exactly one cast at the top.
Continuations in \ineffCEK\ that have no casts at the top correspond
to continuations in \effCEK{C}\ whose casts are identities.
Continuations in \ineffCEK\ that have many casts at the top correspond
to continuations in \effCEK{C}\ where those casts are composed by
$seq(c,c)$.

@@

Fig.~\ref{fig:bisim-SC-D} defines the bisimulation relation
$s_1 \approx s_2$, where $s_1 \in \effCEK{C}$ and $s_2 \in \ineffCEKD{}$.
It is the smallest congruence relation that also includes the
pairs induced by the rules in Fig.~\ref{fig:bisim-SC-D}.
%
One nice aspect of using abstract machines for this proof is that
the expressions in the machine are simply related by syntactic equality.
%
The bisimulation relation is mutually defined on continuations, written $\kappa
\approx \kappa : T$, where $T$ is their source type, and values, written $v 
\approx v : T$, where $T$ is their type.
%
If $k \approx \kappa : T$, adding an identity cast on top of $k$ gives a 
related continuation. This handles the way in which
\effCEK{C} uses $wrap$ to push identity coercions onto continuations
whereas \ineffCEKD{} does not.
%
We remark that this bisimulation relation is unusual in that it uses
some ADT operations in its definition, such as $id$, $cast$, and
$seq$, which is necessary because \effCEK{C} and the bisimulation
is parameterized over the Cast ADT.
%
%\todo[inline]{The use of ``wrap'' obscures this explanation.
%  Consider getting rid of wrap by inlining it. -JS
%\\---\\
%I agree that inlining wrap and ext can improve readability of $\kappa \approx 
%\kappa$, but this would make latex different from Agda, is it alright?
%-KC
%\\---\\
%Yes, that is alright. Inlining is really a trivial change.
%-JS
%}
%
If $\kOOcast{c}{k_1} \approx \kappa_2 : T$, extending the right-hand
side with a cast $T_1 \Rightarrow^l T_2$ and sequencing
$cast(T_1,l,T_2)$ with $c$ on the left-hand side, produces related
continuations. This takes care of the difference between
the transition rules for $e \langle T_1 \Rightarrow^l T_2 \rangle$
on the two machines.

@@

We now come to the main lemma, the weak bisimulation between
\effCEK{C} and \ineffCEKD{}.

\begin{lemma}[Weak Bisimulation between \effCEK{C} and \ineffCEKD{}]
  \label{thm:SD-bisim}
  Assume $C$ implements Lazy D Cast ADT
  and $C$ is a monoid
  and $cast(T,l,T)=id(T)$,
  $s_{1} \in \text{\effCEK{C}}$,
  $s_{2} \in \text{\ineffCEKD}$,
  $s_{1} \approx s_{2}$,
\begin{enumerate}
	\item If $\judgeSreduce{C}{s_1}{s_3}$ then
	$\judgeDreduceTrans{s_2}{s_4}$ and $s_3 \approx s_4$ for some $s_4$.
	\item If $\judgeDreduce{s_2}{s_4}$ then
	$\judgeSreduceTrans{C}{s_1}{s_3}$,
	$\judgeDreduceTrans{s_4}{s_5}$, and
	$s_3 \approx s_5$ for some $s_3$ and $s_5$.
	\item $s_1 = \sOOhalt{o}$ if and only if  $s_2 = \sOOhalt{o}$
\end{enumerate}
%\begin{enumerate}
%  \item $s_1 = \sOOhalt{o}$ if and only if  $s_2 = \sOOhalt{o}$
%%  \item If $s_2 = \sOOhalt{o}$ then $s_1 = \sOOhalt{o}$
%  \item If $\judgeSreduce{C}{s_1}{s_3}$ 
%    then $\judgeDreduce{s_2}{s_4}$ 
%    and  $s_3 \approx^{*} s_4$
%    for some $s_4$
%  \item If $\judgeDreduce{s_2}{s_4}$
%    then $\judgeSreduce{C}{s_1}{s_3}$ 
%    and  $s_3 \approx^{*} s_4$
%    for some $s_3$
%\end{enumerate}
%{\color{red}
%  Jeremy's attempt to reformulate in a more standard way that
%  remains equivalent:
%\begin{enumerate}
%\item If $\judgeSreduce{C}{s_1}{s_3}$ then
%  $\judgeDreducePlus{s_2}{s_4}$ and $s_3 \approx s_4$ for some $s_4$.
%\item If $\judgeDreduce{s_2}{s_4}$ then
%  $\judgeSreduce{C}{s_1}{s_3}$,
%  $\judgeDreduceTrans{s_4}{s_5}$, and
%   $s_3 \approx s_5$ for some $s_3$ and $s_5$.
%\item $s_1 = \sOOhalt{o}$ if and only if  $s_2 = \sOOhalt{o}$
%\end{enumerate}
%}
%Or diagrammatically, 
%  \[\begin{array}{clclc}
%  s_{1} & \longrightarrow_{\text{\effCEK{C}}} & s_1'\\
%  \rotatebox[origin=c]{90}{$\approx$} 
%  & & & \;\;\;\rotatebox[origin=c]{-20}{$\approx$} \\
%  s_{2} & 
%  \longrightarrow_{\text{\ineffCEKD}} & s_2' &
%  \longrightarrow^{*}_{\text{\ineffCEKD}} & s_2'' \\
%  \end{array}\]
\end{lemma}
\begin{proof}
  Part (1) follows from the definition of $s \approx s$.
  Part (2) and (3) are more interesting. 
  By the definition of $s \approx s$, it is straightforward to prove 
  $\judgeSreduce{C}{s_1}{s_3}$ if and only if $\judgeDreduce{s_2}{s_4}$.
  So we can prove two parts together by showing that 
  \[
  \text{if}\; s_{1} \approx s_{2}
  \;\text{and}\;\judgeSreduce{C}{s_1}{s_3}
  \;\text{and}\;\judgeDreduce{s_2}{s_4}
  \;\text{then}\; s_3 \approx^{*} s_4.
  \]
  To put it another way, our goal is to prove that 
  one reduction step in \effCEK{C} corresponds to
  one or more steps in \ineffCEKD.  
  Although there are many cases, the general idea is the same.
  Consider
  \[
  \sOOreturn{\hcvOOcons{v_{11}}{c_{11}}{v_{12}}{c_{12}}}{
    wrap(\kOOcar{\kappa})
  }
  \approx
  \sOOreturn{v_2}{\kOOcar{\kappa}}
  \]

@@

\begin{corollary}[Correctness of \effCEK{C}]
  \label{thm:SD-equiv}
  Suppose $C$ is an instance of the Cast ADT
  and the \lazyD{} ADT, $C$ is a monoid,
  and $cast(T,l,T)=id(T)$.
  If $\judgetype{\emptyset}{e}{T}$ and $o : T$, then
  \[
    \text{\evalEqv{\effCEK{C}}{\ineffCEKD}}
  \]
\end{corollary}
\begin{proof}
	By the definitions of $eval$, we need to show 
	\[
	\judgeSreduceTrans{C}{\sOOinspect{e}{\emptyset}{wrap(\kOOmt)}}{
		\sOOhalt{o}
	}
	\;\text{if and only if}\;
	\judgeSreduceTrans{C}{\sOOinspect{e}{\emptyset}{\kOOmt}}{
		\sOOhalt{o}
	}
	\]
	Obviously, the initial states are related in the bisimulation relation.
	\[
	\sOOinspect{e}{\emptyset}{wrap(\kOOmt)}
	\approx
	\sOOinspect{e}{\emptyset}{\kOOmt}
	\]
	So we can generalize our goal, and prove that if $s_1 \approx s_2$
	\[
	\judgeSreduceTrans{C}{s_1}{\sOOhalt{o}}
	\;\text{if and only if}\;
	\judgeSreduceTrans{C}{s_2}{\sOOhalt{o}}
	\]

@@

\begin{proposition}[Equivalence of Two \lazyD{} Cast ADTs]
  \label{thm:surely-lazyD-eqv}
  Assume $C_1$ and $C_2$ implements Lazy D Cast ADT,
  \[
  eval_{\mathcal{S}(C_1)} = eval_{\mathcal{S}(C_2)}.
  \]
\end{proposition}
\begin{proof}
  Without loss of generality, assume $\judgeSreduce{C_1}{e}{o}$ and prove 
  $\judgeSreduce{C_2}{e}{o}$.\\
  By the definition of $eval_{\mathcal{S}(C)}$, we know 
\[
\judgeSreduceTrans{C_2}{\sOOinspect{e}{\emptyset}{wrap(\kOOmt)}}{\sOOhalt{o}}
\]
  By induction on this reduction sequence and Lemma~\ref{thm:CEKS-bisim}, we 
  have 
\[
\judgeSreduceTrans{C_2}{\sOOinspect{e}{\emptyset}{wrap(\kOOmt)}}{\sOOhalt{o}}
\]
  that is, $\judgeSreduce{C_2}{e}{o}$
\end{proof}

@@

The $L$ cast representation is defined in \figref{fig:L-instance-LazyD}.
Casts in $L$ are lists of steps ($s$), where every step is like a cast in 
\ineffCEKD. The function $applyCast$ applies steps from left to right. Steps are 
restricted by its typing rule such that its source and target are different. This 
restriction is necessary to show $cast(T,l,T) = id(T)$. With this representation
of casts, the operator $id$ produces an empty list of steps
and $seq$ appends two lists of steps.

@@

\begin{lemma}[$L$ is Correct wrt. \ineffCEKD]
  \label{lem:L-correct}
  If $\judgetype{\emptyset}{e}{T}$ and $o : T$, then
  \[
  \text{\evalEqv{\effCEK{L}}{\ineffCEKD}}
  \]
\end{lemma}
\begin{proof}
  Immediately from
  Correctness of \effCEK{C} (Lemma~\ref{thm:SD-equiv}) and 
  Properties of $L$ (Proposition~\ref{thm:L-LazyD-monoid}).
\end{proof}

@@

  \fbox{$applyMiddle(v,\ell,m) = r$}
  \[
  \begin{array}{rclr}
  \funrule{applyMiddle(\hcvOOtt,\ell,\POOunit)}{\rOOsucc{\hcvOOtt}}{}
  \funrule{applyMiddle(\hcvOOfun{c_1}{\mathcal{E}}{x}{e}{c_2},\ell,\POOfun{c_3}{c_4})}{
    \rOOsucc{(\hcvOOfun{(c_3 \fatsemi^\ell c_1)}{\mathcal{E}}{x}{e}{(c_2 
    \fatsemi^\ell c_4)})}
  }{}
  \funrule{applyMiddle(\hcvOOcons{v_1}{c_1}{v_2}{c_2},\ell,\POOprod{c_3}{c_4})}{
    \rOOsucc{(\hcvOOcons{v_1}{(c_1 \fatsemi^\ell c_3)}{v_2}{(c_2 
    \fatsemi^\ell c_4)})}
  }{}
  \funrule{applyMiddle(\hcvOOinl{v}{c_1},\ell,\POOsum{c_3}{c_4})}{
    \rOOsucc{(\hcvOOinl{v}{(c_1 \fatsemi^\ell c_3)})}
  }{}
  \funrule{applyMiddle(\hcvOOinr{v}{c_2},\ell,\POOsum{c_3}{c_4})}{
    \rOOsucc{(\hcvOOinr{v}{(c_2 \fatsemi^\ell c_4)})}
  }{}
  \funrule{applyMiddle(v,l,m)}{
    \rOOfail{l}
  }{
    \sidecond{v \not\smile m}
  }
  \end{array}
  \]

@@

We also present steps toward the first framework for proving the
correctness of cast representations.
%
The framework includes abstract data types for cast representations
(Cast ADT and its refinement Lazy D Cast ADT), a parameterized abstract machine
\effCEK{C}, and a theorem which states that \effCEK{C} is equivalent
to $\ineffCEKD{}$ when $C$ is a Lazy D Cast ADT.
%
%The Lazy D Cast ADT refines the Cast ADT. 
%
We conjecture that Lazy D
threesomes and Lazy D coercions in normal form are instances of the
Lazy D Cast ADT.
